### 2021-09-16 sections/appendix/descrete_event_simulation/main.tex
Add Reference and Explanation section

\subsection{Reference}

@@

For every service completion Ciw stores all data records in a simulation 
object~\cite{ciwpython}.
For the specific library the records that are stored, along with the 
range of values that they can take are as follows:

>>>>

\subsection{Reference}
The primary tool that was used in the construction of the discrete event 
simulation model was the python library \texttt{ciw}.
See Ciw's documentation for a more detailed explanation of how it works and 
what are its capabilities~\cite{ciwpython}.

Find below a detailed list of the functions that were created for the simulation
model:

\begin{itemize}
    \item \lstinline[style=pystyle]{build_model}: \textit{Builds a ciw object 
    that represents a model of a queuing network with two service centres.}
    \item \lstinline[style=pystyle]{build_custom_node}: \textit{Build a custom 
    node to replace the default ciw.Node. Inherits from the original ciw.Node 
    class and replaces two methods.}
    \item \lstinline[style=pystyle]{simulate_model}: \textit{Simulate the model
    by using the custom node and returning the simulation object}
    \item \lstinline[style=pystyle]{get_simulated_state_probabilities}: \textit{
    Calculates the vector pi in a dictionary format or an array format}
    \item \lstinline[style=pystyle]{extract_times_from_records}: \textit{Get the
    required times (waiting, service, blocking) out of ciw's records where all 
    individuals are treated the same way}
    \item \lstinline[style=pystyle]{extract_times_from_individuals}: \textit{
    Extract waiting times and service times for all individuals and proceed to 
    extract blocking times for just class 2 individuals}
    \item \lstinline[style=pystyle]{get_list_of_results}: \textit{Modify the 
    outputs so that they are returned in a list format where it is sometimes 
    easier to be used by other functions.}
    \item \lstinline[style=pystyle]{get_multiple_runs_results}: \textit{Get the 
    waiting times, service times and blocking times for multiple runs of the 
    simulation}
    \item \lstinline[style=pystyle]{get_average_simulated_state_probabilities}:
    \textit{This function runs \hfill\break
    get\_simulated\_state\_probabilities for multiple iterations to eliminate 
    any stochasticity from the results}
    \item \lstinline[style=pystyle]
    {get_mean_blocking_difference_between_two_systems}: \textit{Given a 
    predefined proportion of class's 2 arrival rate calculate the mean 
    difference between blocking times of two systems with a given set of 
    parameters}
    \item \lstinline[style=pystyle]{calculate_class_2_individuals_best_response}
    \textit{Obtains the optimal distribution of class 2 individuals such that 
    the blocking times in the two systems are identical and thus minimised}
    \item \lstinline[style=pystyle]
    {extract_total_individuals_and_the_ones_within_target_for_both_classes}:
    \hfill\break \textit{Extract the total number of individuals that pass 
    through the model and the total number of individuals that exit the model 
    within the given target.}
    \item \lstinline[style=pystyle]
    {get_mean_proportion_of_individuals_within_target_for_multiple_runs}: 
    \textit{Get the average proportion of individuals within target by running 
    the simulation multiple times}
\end{itemize}

@@

Based on Ciw's functionality the simulation model stores all data records in a
Record object. 
For every event that takes place a record is created with all the relevant
information.
For this specific library, the records that are stored, along with the 
range of values that they can take are as follows:
